\documentclass{screenplay}
\usepackage{fontspec}
\setromanfont[
BoldFont=Courier Prime Sans Bold.ttf,
ItalicFont=Courier Prime Sans Italic.ttf,
BoldItalicFont=Courier Prime Sans Bold Italic.ttf
]{Courier Prime Sans.ttf}
\usepackage{microtype}

\title{hug}
\author{Clement Lee}
\address{clementlee0@gmail.com}
\begin{document}
% \coverpage
\fadein
\extslug[night]{Snowstorm}
The background fades in, but the title stays, showing a wide shot of an icy blizzard and a little hut covered in snow.
As the wind howls, the BOY and the GIRL (of apparent ages roughly 10 and 5, respectively) slowly walk towards the hut, leaving deep footprints, and carrying firewood.

The GIRL falls into a patch of snow and yelps.
The BOY immediately drops his bundle and picks her up, giving her a warm hug.
The GIRL smiles as she cuddles in for warmth.

Suddenly, the door to the hut opens, revealing a warm interior with a crackling fire.
The BOY and the GIRL pick up their bundles, and begin to head towards the door.
The FATHER bursts into the doorway, clearly drunk and enraged.

As the BOY and the GIRL walk in with heads down, the FATHER angrily grabs the door and slams it shut behind him, walking in with lumbering steps.
From the outside, muffled undiscernable shouts from the FATHER are heard continually as the narration progresses.

Suddenly, the door opens, and the BOY and the GIRL are thrown out into the snow by the FATHER.
He also begins to throw out some small things that belong to them, but remains unseen inside the hut.
After their belongings (among them containing the BOY's hooded cape and the GIRL's scarf) are scattered in the snow, the FATHER appears at the doorway, brandishing a hunting knife.

As the BOY looks on, the FATHER glares at the GIRL, wielding the knife.
Without provocation, he throws it at her.
The BOY, in slow motion, gets up and dives for the knife and just barely catches it.
He falls into the snow, and as he opens his hand, it's revealed to have given him a deep slice, dripping blood into the snow.

The BOY looks up at the FATHER, but the FATHER just walks back into the hut.
A few moments later, the FATHER reemerges, but only to slam the door shut again.

The GIRL shuffles over the BOY, and carefully begins bandaging his hand using her scarf.
When he resists, she becomes more insistent, until the job is done.
The BOY then covers her in his cape as they solemnly gather their belongings and trudge away from the hut.
\extslug[sunrise]{Snowy wasteland}
Extreme long shot of the BOY and GIRL, moving slowly a snowy plain.
The BOY still has the scarf wound around his hand, and the GIRL is still wearing his cape.
Their heads are down, but as the sun rises, they look up enthralled as the camera comes close.

As they keep walking, fade into the next scene maintaining the same shot.

\extslug[morning]{Mountains}
The BOY and the GIRL have aged by a few years---their clothing is a little more ragged, and they have grown in size.
They walk on the top of a mountain as the sun comes into full view, covering the mountains in golden light.
The BOY and the GIRL disappear as they begin to head down the mountain, as we fade into the next scene and the camera pans out.

\extslug[noon]{Forest}
The light streams down into a beautiful forest as the camera dives into the trees.
The BOY, yet again a little older, sits down on a mossy rock near a stream, and begins unwinding the scarf, which is bloodstained but otherwise well-maintained.
It's clear that this is a common ritual for him.
As the bindings fall away, it's revealed that the BOY has a deeply set scar from the knife.
He plunges his hand into the stream, wincing a little, but relaxing after a moment.

The GIRL comes over, bursting with energy and clasping something in her hands.
She shows the BOY, and though it is just a pinecone, they smile as he stands up, and wraps his hand again as they begin to walk away.
The camera follows behind them, and maintains the same shot into the next scene.

\extslug[afternoon]{Plains}
With a burst of light, the BOY and the GIRL reach the edge of the forest looking into the golden plains.
They've both aged again; the BOY is a mature young adult of roughly 18, and the GIRL is now 13 but still maintains a na{\"i}ve energy.
The BOY now wears the scarf around his neck, and the cape wraps around the GIRL's waist.

%\theend
\end{document}
